\documentclass[10pt,letterpaper]{article}
\begin{document}
\title{CHIPS SELLING IN MAKERERE KIKONI}
\author{by BAMWIREKU PRISCA   \\ 216020499 \\  16/U/18716}
\maketitle
\section{Introduction }
I came to learn that chips is the kind of food eaten mostly by people who leave in kikoni. Given the fact that most of the people who live there are students, I came to learn that most of them hate cooking. They therefore opt for quick food like chips.
\section{Problem statement }
The purpose of this study was to assess the most kind of food eaten in Makerere Kikoni
\section{Objectives of the study}
1.To identify the reasons why chips is widely preferred to all other foods.
2.To assess the most kind of food eaten in Makerere Kikoni

\section{Scope of the study}
This study was limited to only sellers of chips in Makerere Kikoni 
\section{Method of study}
I went on ground for around a week. I noticed that people mostly buy the chips in the evening. I also tried to interview some lady who responded to all wat I asked. First and foremost, she told me that people mostly buy chips in the evening. She then went further more and told me that the number of girls who buy the chips is much bigger than the number of boys. I got to know that it is sold in a variety of prices and quantities.
\section{Limitations of the study}
To This study was limited by the untrustworthy clients whom I tried to interview as some gave me wrong feedback. Furthermore, some clients didn’t want to interact with me wholesomely.
It turns out to be a basic method of research because I just gathered knowledge about chips selling. Since my research is based on facts I gathered from the field, it turns out to be an analytical method of research.



\end{document}